\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,margin=2cm,landscape]{geometry}

\usepackage{parskip}
\setlength{\parindent}{0pt}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue
}

\begin{document}
\begin{minipage}[t]{0.24\linewidth}
\section*{Michael Lewis Boyles}

\vspace{0.2cm}I’m a software developer with a passion for writing great software. I’m outgoing, self-motivated and ambitious. I’m an advocate for open-source software, object-oriented programming and XP practices. 

\vspace{0.2cm}I’ve always had a natural aptitude for programming and consistently received excellent grades in the programming modules I studied as part of my degree.

\vspace{0.2cm}I pride myself on my ability to communicate ideas well and am always happy to help others. In my spare time I enjoy answering questions on StackOverflow, where I have 30k reputation points, mostly in the Java tag.

\vspace{0.2cm}I’ve led successful teams in both my professional and academic life, as well as functioned as a helpful and productive team member. I also work well independently, as I was required to do when freelancing.

\vspace{0.2cm}Aside from the Internet and technology, my big passion is music. I play guitar and bass, and sometimes record. I’m also enthusiastic about film and photography.

\vspace{0.2cm}Thanks for considering my application. I hope to hear from you soon.

\section*{Get In Touch}

W: \href{https://boyl.es}{https://boyl.es}\\
E: \href{mailto:michael@boyl.es}{michael@boyl.es}

\end{minipage}
\hspace{0.5cm}
\begin{minipage}[t]{0.35\linewidth}
\section*{Apr 2017 - Present}
\textbf{Senior Developer}\\
BGC Partners

\vspace{0.3cm}Java, Spring Boot, Oracle, JavaScript, React

\vspace{0.3cm}I’ve been responsible for developing and extending BGC and GFI Electronic and Hybrid Trading Systems, one for fixed income, and one for FX. Mostly I’ve been building FIX API transformers: microservices which allow clients to interface with our trading systems without implementing our spec. As part of this, I contributed to the design and development of an annotation-based framework built around QuickFIX/J. These FIX transformers are Spring Boot projects which make heavy use of Java 8 features and are built with Maven via Bamboo. I’ve developed these services for a number of 3rd party buy-side execution and order management systems and investment banks.

\section*{Sep 2015 - Apr 2017}
\textbf{Graduate Software Engineer}\\
Hewlett Packard Enterprise

\vspace{0.3cm}After graduating, I worked on a mission planning system used by the RAF. This legacy system was developed in C, C++ and Python, following the Scrum methodology. We followed rigorous development practices: unit/integration testing, static analysis, code reviews, performance profiling.

\vspace{0.3cm}I was selected as part of a very small team to design a prototype v2 in Java to be used as part of a pitch for additional investment. The tech lead of this project was impressed with my work and described it as outstanding.
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[t]{0.35\linewidth}
\section*{2013 - 2014}
\textbf{Web Developer}\\
West Digital Marketing

\vspace{0.3cm}PHP, HTML5, JavaScript, MySQL

\vspace{0.3cm}An industry placement between the second and third year of my degree. The job involved , email marketing and web design and development.

\section*{2011 - 2015}
BSc (Hons) Computer Science - First Class\\
\textbf{Newcastle University}

\vspace{0.3cm}The course was primarily taught in Java, with a strong theoretical background. I studied modules in cryptography, graphics (OpenGL) and networking. I was also presented with the Netcraft Programming Award for achieving amongst the highest marks in the programming modules in first year. In second year I was the leader of a software engineering team project in which I was able to lead the team to a high first class mark in the module.

\section*{Technologies}

\textbf{Languages:}\\
\textbf{Advanced:} Java, \textbf{Proficient:} JavaScript, C++, PHP

\textbf{Web:} JavaScript, React, HTML, Sass\\
\textbf{Databases:} Oracle, MySQL, DynamoDB\\
\textbf{OS:} Windows, Linux
\end{minipage}

\end{document}
